### 2014-02-27 paper/concrete.tex

\begin{theorem}[Isomorphism preserves termination sensitive non-interference]
    Consider a language \tar{L} with configurations |tc|, reduction
    relation \tar{|.->|} and erasure function \tar{|erasef l|} and a
    language \ifc{L} with configurations |ic|, reduction relation
    \ifc{|.->|} and erasure function \ifc{|erasef l|}.  We say that
    \tar{L} and \ifc{L} are isomorphic if there exist (total) functions
    $f : |tc -> ic|$ and $f^{-1} : |ic -> tc|$ such that $f \circ f^{-1}
    = id$, $f^{-1} \circ f^{-1} = id$, and that $f$ and $f^{-1}$ are
    functorial over $l$-equivalences (i.e. if $|tc|\ \tar{\approx_l}\
    |tc'|$ then $f(|tc|)\ \ifc{\approx_l}\ f(|tc'|)$ and vice-versa).
    Then if \ifc{L} satisfies termination sensitive non-interference,
    then \tar{L} satisfies termination sensitive non-interference.
\end{theorem}

\begin{proof}
    Easy application of TSNI \tar{L} by applying $f$
\end{proof}

>>>>

\begin{definition}[Information-flow control language]
    An information-flow control language L is a tuple $(|C|, |C|^*, |.->|,
    |erasef l|)$, where $c \in |C|$ is the type of machine configurations,
    $|C|^*$ is the type of erased machine configurations, |.->| is a
    reduction relation between machine configurations and $|erasef l|$
    is an erasure function from machine configurations to erased machine
    configurations.
\end{definition}

\begin{definition}[$l$-equivalence]
    Two machine configurations $c$ and $c'$ are considered $l$-equivalent ($c \approx_l c'$)
    if $|erase l c| = |erase l c'|$.
\end{definition}

\begin{definition}[Isomorphism of information-flow control languages]
    Two languages
    \tar{L} $(|tC|, |tC|^*, \tar{|.->|}, \tar{|erasef l|})$ and \ifc{L} $(|iC|, |iC|^*, \ifc{|.->|}, \ifc{|erasef l|})$ are isomorphic if there exist (total) functions
    $f : |tC -> iC|$ and $f^{-1} : |iC -> tC|$ such that $f \circ f^{-1}
    = id_{|tC|}$, $f^{-1} \circ f = id_{|iC|}$, and that $f$ and $f^{-1}$ are
    functorial over $l$-equivalences (i.e. if $|tc|\ \tar{\approx_l}\
    |tc'|$ then $f(|tc|)\ \ifc{\approx_l}\ f(|tc'|)$ and vice-versa).
\end{definition}

\begin{theorem}[Isomorphism preserves termination sensitive non-interference]
    If \ifc{L} is isomorphic to \tar{L} and \ifc{L} satisfies TSNI, then
    \tar{L} satisfies TSNI.
\end{theorem}

\begin{proof}
    Easily shown by transporting configurations and reduction derivations
    from \tar{L} to \ifc{L}, applying TSNI, and then transporting the resulting
    configuration and multi-step derivation back.
\end{proof}
